The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Updates to Section 3 of FThresholds paper

Given a rational number $t$ and  an element $f$ of a $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, 
the command {\tt isFPT(t, f)} checks whether $t$ is the $F$-pure threshold of $f$.  
In general, this is done by computing the \emph{test ideal} associated to the pair $(R, f^t)$, and that associated when $t$ is replaced with a value less than $t$ that is very close to $t$, that associated to the pair $(R, f^{t-\epsilon}s)$. 
These values are computed using the functions 
{\tt testIdeal} and {\tt FPureModule} from the \emph{TestIdeals} package
(CITE THE TEST IDEALS PACKAGE PAPER).
In fact, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^{t-\epsilon})$ is $R$, but  $\tau(R, f^t)$ is a proper ideal.  
Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\epsilon})$.  \textcolor{red}{These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.}

The function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$.  Namely, 
{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, $0$ when $t = \fpt(f)$ and $1$ when $t > \fpt(f)$.

Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : loadPackage "FThresholds"

i2 : R = ZZ/2[x,y,z];

i3 : f = x^2+y^5+z^5;

i4 : isFPT(1/2, f)

o4 = true

i5 : isFPT(1/3, f)

o5 = false

i6 : compareFPT(3/4, f)

o6 = 1
\end{MyVerbatim}
}
\medskip

The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
\[
\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).
\]
Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.

>>>>

The \emph{FThresholds} package contains methods to 
 test candidate values for an $F$-pure threshold, and even $F$-jumping numbers, even in some singular rings.  
Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a rational number $t$ and an element $f$ of $R$, the command {\tt isFPT(t,f)} outputs {\tt true} if $t$ is the $F$-pure threshold of $f$, and {\tt false} otherwise. 
Moreover, the function {\tt compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely, 
{\tt compareFPT(t, f)} returns {\tt-1} when $t < \fpt(f)$, {\tt 0} when $t = \fpt(f)$ and {\tt 1} when $t > \fpt(f)$.
Setting the option {\tt IsLocal} to {\tt true} tells the function to consider the $F$-pure threshold at the origin.
The following example illustrates this functionality.

i1 : R = ZZ/11[x, y, z]/( x^2 - y*( z - 1 ) );

i2 : compareFPT( 5/11, z - 1 )

o2 = -1

i3 : isFPT( 1/2, z - 1 )

o3 = true

i4 : isFPT( 1/2, z - 1, IsLocal => true )

o4 : false

The general method applied calls upon functionality from the \emph{TestIdeals} package (CITE).  The functions {\tt testIdeal} and {\tt FPureModule} therein are used
to compute the test ideals of $f$ with respect to the parameter $t$, and that with respect to $t - \varepsilon$, for $\varepsilon>0$ very small. For instance, as noted in the introduction, when $R$ is a polynomial ring, $t$ is the $F$-pure threshold of $f$ if and only if $\tau(R, f^t)$ is contained in the homogeneous maximal ideal, but 
$\tau(R, f^{t-\varepsilon})$ is not. 
Note that when $R$ is a strongly $F$-regular Gorenstein ring, {\tt FPureModule(t, f)} precisely computes $\tau(R, f^{t-\varepsilon})$.  
%These commands work more generally, but they \emph{only} currently work when $R$ is $\bQ$-Gorenstein, with index not divisible by $p$.

Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.
Analogous syntax is used, as shown in the following example.

i49 : R = ZZ/13[x, y];

i50 : f = y*( ( y + 1 ) - ( x - 1 )^2 )*( x - 2 )*( x + y - 2 );

i51 : isFJumpingExponent( 3/4, f )

o51 = true
